### 2021-07-10 src/paper/results/fit.tex
Temp.

This section compares simulated data from our model with empirical data from Germany. We
look at observed infections, fatality rates,\comment[id=K]{should we include them?} the
spread of the B.1.1.7 mutation, vaccinations\comment[id=K]{We fit vaccinations in the
population by construction. Maybe this should go to a different section?} and rapid test
demand. Where available we do not only look at aggregated statistics but also analyze the
model fit for age groups and federal states.

% summary of the fit
Overall, our model achieves an excellent fit of the two waves of infections with few free
parameters (Figure~\ref{fig:aggregated_fit2}. As a result the effective replication
number is similar to that reported by the Robert Koch-Institut (see
Figure~\ref{fig:fit_r_effective}). This excellent fit is also achieved for most age
groups in Germany. The fit is also good for many German federal states even though our
synthetic population does not represent the differences in the distribution of age groups
and they only had a small weight in the optimization. Despite, the fact that the number
of performed rapid tests and their distribution in the population results endogenously
inside our model we fit the share of the population with at least a weekly rapid test
very well and err on the side of too few individuals that have ever done a rapid test.

% observed infections
Our fit of the infection rates in Germany between October 2020 and June 2021 is very
good. The incidence in our model follows the shape of the reported incidence almost
perfectly. The increase in December is somewhat less steep than it was. This can be
attributed to the large number of cases in nursing homes during that time that our model
cannot capture because it does not include nursing homes. It is very noticeable that high
levels of infections often coincide with increased statistical uncertainty, as for
example in April and May.

@@

% observed infections by age group
Zooming into the different age groups in Figure~\ref{fit:age_group_fit}, we can see that
our model is also able to reproduce the infection rates on this level. Differences
between the age groups allow us to identify the infection probabilities because different
age groups have contacts of different types (e.g. Mostly children go to school, the share
of workers is highest in the 35 to 59 age bracket etc.). There are three exceptions to
our fit. Firstly, the age group of 80 to 100 year olds due to the absence of nursing
homes in our synthetic population. Secondly, the increase in adolescents in April. It is
surprising that we do not match this increase despite explicitly modeling the
introduction of rapid tests for students. However, it can be expected that every rapid
test in a school setting is followed up by a PCR test while only 82\% of our population
\citep{Betsch2021} demand a confirming PCR test when receiving a positive rapid test. The
last age group where our fit does not fit the empirical curve very well is the group of
15 to 34 year olds. This group has been touted to have a very active social life and it
has often been suspected that this age group also stayed more socially active during the
pandemic. Since our model does not include either effect it's unsurprising that the
actual case numbers in this group are consistently higher than our simulated case
numbers.\comment[id=K]{Does anyone have an idea why we do not match the shape from Oct to
Dec?}

@@

\begin{figure}[ht]     % rapid test demand
    \centering
    \caption{Share of Individuals With Rapid Tests}
    \label{fig:share_ever_rapid_test}
    \begin{subfigure}{.55\textwidth}
        \includegraphics[width=0.9 \textwidth]{figures/results/figures/scenario_comparisons/combined_fit/full_share_ever_rapid_test}
        \caption{Share of Individuals That Have Ever Done a Rapid Test}
    \end{subfigure}%
    \begin{subfigure}{.55\textwidth}
        \includegraphics[width=0.9 \textwidth]{figures/results/figures/scenario_comparisons/combined_fit/full_share_rapid_test_in_last_week}
        \caption{Share of Individuals Having Done a Rapid Test in the Last Week}
    \end{subfigure}
    \label{fig:share_rapid_test_last_week}
    \floatfoot{\noindent \textit{Note:} The figure compares the share of individuals who
        have ever done a rapid test or done a rapid test within the last week in our
        simulations to the shares reported in the
        \href{https://projekte.uni-erfurt.de/cosmo2020/web/topic/wissen-verhalten/80-schnelltests/}{COVID-19
        Snapshot Monitoring Survey}. The left panel compares the share of individuals who
        have ever done a rapid test. The right panel compares the share of individuals
        who have done a rapid test within the last seven days in our simulation compared
        to the share reporting to have done at least weekly rapid tests in the last four
        weeks in the COSMO survey. Overall our calibration of rapid tests are slightly
        conservative. The overall share is below that in the study. We fit the share of
        weekly tests quite exactly. However, the study only covers adults while our share
        also includes children who are tested very regularly when attending school.}
\end{figure}

>>>>

%%% WRITE MORE POSITIVELY

This section compares simulated data from our model with empirical data from Germany. We
look at observed infections, the spread of the B.1.1.7 mutation,
vaccinations\comment[id=K]{We fit vaccinations in the population by construction. Maybe
this should go to a different section?} and rapid test demand. Where available we do not
only look at aggregated statistics but also analyze the model fit for age groups and
federal states.

% summary of the fit
Overall, our model achieves an excellent fit of the two waves of infections with few free
parameters (Figure~\ref{fig:aggregated_fit2}. As a result the effective replication
number is similar to that reported by the RKI (see Figure~\ref{fig:fit_r_effective}).
This excellent fit is also achieved for most age groups in Germany. The fit is also good
for many German federal states. Despite, the fact that the number of performed rapid
tests and their distribution in the population results endogenously inside our model we
fit the share of the population with at least a weekly rapid test very well and err on
the side of too few individuals that have ever done a rapid test.

% observed infections
Our fit of the infection rates in Germany between October 2020 and June 2021 is very
good. The incidence in our model follows the shape of the reported incidence almost
perfectly. % The increase in December is somewhat less steep than it was. This can be
% attributed to the large number of cases in nursing homes during that time that our
% model cannot capture because it does not include nursing homes. \comment[id=K]{Write
% about uncertainty and that we take enough simulations to have a stable mean}

@@

% observed infections by age group
Zooming into the different age groups in Figure~\ref{fig:age_group_fit}, we can see that
our model is also able to reproduce the infection rates on this level. Differences
between the age groups allow us to identify the infection probabilities because different
age groups have contacts of different types (e.g. Mostly children go to school, the share
of workers is highest in the 35 to 59 age bracket etc.). There are only three
\textcolor{red}{\ldots}. Firstly, the age group of 80 to 100 year olds due to the absence
of nursing homes in our synthetic population. Secondly, the increase in adolescents in
April. It is surprising that we do not match this increase despite explicitly modeling
the introduction of rapid tests for students. However, it can be expected that every
rapid test in a school setting is followed up by a PCR test while only 82\% of our
population \citep{Betsch2021} demand a confirming PCR test when receiving a positive
rapid test. The last age group where our fit does not fit the empirical curve very well
is the group of 15 to 34 year olds. This group has been touted to have a very active
social life and it has often been suspected that this age group also stayed more socially
active during the pandemic. Since our model does not include either effect it's
unsurprising that the actual case numbers in this group are consistently higher than our
simulated case numbers.\comment[id=K]{Does anyone have an idea why we do not match the
shape from Oct to Dec?}

@@

\begin{figure}[ht]     % rapid test demand
    \centering
    \caption{Share of Individuals With Rapid Tests}
    \label{fig:share_ever_rapid_test2}
    \begin{subfigure}{.55\textwidth}
        \includegraphics[width=0.9 \textwidth]{figures/results/figures/scenario_comparisons/combined_fit/full_share_ever_rapid_test}
        \caption{Share of Individuals That Have Ever Done a Rapid Test}
    \end{subfigure}%
    \begin{subfigure}{.55\textwidth}
        \includegraphics[width=0.9 \textwidth]{figures/results/figures/scenario_comparisons/combined_fit/full_share_rapid_test_in_last_week}
        \caption{Share of Individuals Having Done a Rapid Test in the Last Week}
    \end{subfigure}
    \label{fig:share_rapid_test_last_week2}
    \floatfoot{\noindent \textit{Note:} The figure compares the share of individuals who
        have ever done a rapid test or done a rapid test within the last week in our
        simulations to the shares reported in the
        \href{https://projekte.uni-erfurt.de/cosmo2020/web/topic/wissen-verhalten/80-schnelltests/}{COVID-19
        Snapshot Monitoring Survey}. The left panel compares the share of individuals who
        have ever done a rapid test. The right panel compares the share of individuals
        who have done a rapid test within the last seven days in our simulation compared
        to the share reporting to have done at least weekly rapid tests in the last four
        weeks in the COSMO survey. Overall our calibration of rapid tests are slightly
        conservative. The overall share is below that in the study. We fit the share of
        weekly tests quite exactly. However, the study only covers adults while our share
        also includes children who are tested very regularly when attending school.}
\end{figure}
